Future challenges for Research Software Engineering

### 2025-05-09 future_challenges_for_RSEng.tex
Update future_challenges_for_RSEng.tex
Co-authored-by: Jan Philipp Thiele <54978337+jpthiele@users.noreply.github.com>
Add reminder for citing groups paper

RSEs can either be embedded in research groups (belonging to the mid-level university staff),
or be part of larger RSE units.
The participants had the opinion that focusing on embedded RSEs would make onboarding new RSEs to existing projects easier.
This, however, comes with additional funding challenges,
as long-term funding is more difficult to acquire in lower levels of an organization.
Third-party funding can mitigate this issue in the mid-term.
However, the participants considered central RSE groups more likely in the future,
due to the fact that there are already examples and activities from various universities in this direction
(examples include the univerisities of Jena, Heidelberg, Göttingen).
We expect funding in central groups to evolve from initially temporary positions to permanent positions,
as the groups themselves prove themselves valuable.
Embedded RSEs and central groups will need to network with each other,
and potentially request and coordinate support from external RSEs.

>>>>

RSEs can either be embedded in research groups (belonging to the mid-level university staff),
or be members of larger RSE units. (TODO: Cite RSE groups paper)
The participants had the opinion that focusing on embedded RSEs would make onboarding new RSEs to existing projects easier.
This, however, comes with additional funding challenges,
as long-term funding is more difficult to acquire in lower levels of an organization.
Third-party funding can mitigate this issue in the mid-term.
However, the participants considered central RSE groups more likely in the future,
due to the fact that there are already examples and activities from various universities in this direction
(examples include the universities of Jena, Heidelberg, Göttingen).
We expect funding in central groups to evolve from initially temporary positions to permanent positions,
as the groups themselves prove themselves valuable.
Embedded RSEs and central groups will need to network with each other,
and potentially request and coordinate support from external RSEs.
